\chapter{Conclusion}\label{chap:conclusion}
As this exploration of MTMCT concludes, it is clear that the field is still navigating complex challenges and evolving demands. This journey, through the exploration of various methodologies, their inherent limitations, and prospective future directions, paints a comprehensive picture of the current state and potential evolution of MTMCT especially in the context of online and real-time environments.

While frameworks like R-CNN, YOLO, SORT, and DeepSORT have advanced intra-camera tracking, their limitations in inter-camera environments underscore the specific challenges of MTMCT. These challenges include the need for effective inter-camera tracking, robust data association across varied camera views, and maintaining consistent tracking accuracy in diverse and dynamic environments.

The integration of MTMCT with emerging technologies such as edge computing and IoT presents exciting opportunities to enhance the scope and effectiveness of tracking systems. These integrations could lead to more comprehensive and versatile systems, capable of handling the demands of real-time tracking in various applications, from urban surveillance to traffic management and public safety.

However, the advancement of MTMCT technologies also brings to the forefront the need for careful consideration of ethical and privacy issues. As the capabilities of MTMCT systems expand, ensuring their responsible use and addressing the societal implications of widespread surveillance are important. This involves developing frameworks that respect individual privacy and addressing the broader societal impacts of these technologies.

In summary, MTMCT stands as a field with significant potential and will impact a wider range of sectors as it already does. The path forward involves not only technological innovation but also a collaborative approach that includes researchers, technologists, policymakers, and ethicists. By addressing current limitations and exploring new horizons, MTMCT can achieve new levels of efficiency and accuracy, marking a new era of sophisticated and responsible tracking systems.